Article Title

### 2013-12-27 plos.tex
rev34. Made Supp Fig. 2 smaller by keeping only comparisons to C_{sparse+latent}

In this study, we sought most statistically efficient estimators of neural correlations in recordings from large, dense groups of cortical neurons.  Using fast 3D random-access laser scanning microscopy of calcium signals, we recorded the activity of nearly every neuron in volumes of about 200 $\mu$m wide and 100 $\mu$m deep (150--350 cells) in mouse visual cortex.  We hypothesized that in these dense recordings, the correlation matrix would be most efficiently represented by a sparse network of partial correlations between pairs of observed neurons combined with common latent factors representing unobserved inputs and global network fluctuations.  Indeed, in cross-validation tests, the covariance matrix estimator based on such approximations outperformed other regularized estimators. Mirroring previously described patterns of synaptic connectivity, the density of positive partial correlations decreased rapidly with both physical distances and preferred orientation differences whereas negative partial correlations were less selective.  The inferred functional connectivity obtained using these methods can generate hypotheses about synaptic architecture that can guide future experimental work.

@@

Pearson correlations between the spiking activity of pairs of neurons, or simply \emph{neural correlations}, are among the most familiar descriptive statistics of neural population activity \cite{Averbeck:2006, Zohary:1994, Kohn:2005, Bair:2001, Ecker:2010}.  For example, \emph{noise correlations}, \emph{i.e.}~the correlations of trial-to-trial response variability between pairs of neurons, have a profound impact on stimulus coding \cite{Zohary:1994, Abbott:1999, Sompolinsky:2001, Averbeck:2006, Josic:2009, Berens:2011, Ecker:2011}. In addition, noise correlations and correlations in spontaneous activity have been hypothesized to reflect key features of functional connectivity in neural circuits.  This interpretation is supported by a series of discoveries of nontrivial relationships between neural correlations and other aspects of circuit organization such as the physical distances between neurons \cite{Smith:2008,Denman:2013}, their synaptic connectivity \cite{Ko:2011},  stimulus response similarity \cite{Bair:2001, Arieli:1995, Chiu:2002, Kenet:2003, Kohn:2005, Cohen:2008, Cohen:2009, Ko:2011, Smith:2013b}, cortical layer specificity \cite{Hansen:2012,Smith:2013}, progressive changes in development and in learning \cite{Golshani:2009,Gu:2011}, changes due to sensory stimulation and global brain states \cite{Goard:2009, Kohn:2009, Ecker:2010, Renart:2010}, and others.

@@

\paragraph{Additional information in neural correlation matrices}
Yet, a complete correlation matrix provides more information than the equivalent number of isolated pairwise correlations. In early studies, the effects of correlations were extrapolated from isolated pairs to entire populations through simulation and theoretical analysis \cite{Shadlen:1998, Zohary:1994}. In contrast, modern multineuronal recordings from increasingly large and dense populations of highly interconnected neurons allow estimation of various low-dimensional representations of the entire correlation matrix, which can enable inquiry into the nature of underlying physiological mechanisms and computational principles.

For example, one form of low-dimensional representation of the correlation matrix is its low-rank approximation. Such approximations are particularly suitable for capturing shared fluctuations across the recorded population. Low-rank components can be extracted using principal component or factor analysis. The resulting structure of  neural correlations has been analyzed in a number of studies with particular attention paid to their temporal dynamics \cite{Yu:2009}.

@@

Conditional independence between a pair of variables suggests a lack of direct interaction between the underlying processes. Therefore, networks of partial correlations (sometimes called \emph{association networks}) can be used to infer interactions between the components of a complex system.  This approach has been used to uncover the structure of gene interaction networks \cite{Schafer:2005,Peng:2009} and the functional connectivity between brain regions from fMRI signals \cite{Varoquaux:2012,Ryali:2012}. In \emph{elliptical distributions} (those of the form $x \sim \frac 1 Z g\left((x-\mu)^\T\Sigma^{-1}(x-\mu)\right)$, where $g$ is an arbitrary function, $Z$ is the scalar normalizer, $\Sigma$ is the covariance matrix) and the multivariate normal distribution in particular, interactions are completely defined by linear effects and partial correlations express conditional dependencies. A multivariate normal distribution specified by a weighted graph of non-zero partial correlations is known as a Gaussian Graphical Model or Gauss-Markov Random Field \cite{Koller:2009}. With departure from linearity, the correspondence between conditional dependence and partial correlations diminishes and can break down \cite{Loh:2012}. For example, the coupling terms in pairwise Ising models have no direct relationship to the partial correlations \cite{Schneidman:2006, Tkacik:2006}.

@@

The true correlation matrix is the normalized version of the true covariance matrix defined as
\begin{equation}\label{eq:true-covariance}
    \Sigma = \E{(x-\mu)(x-\mu)^\T},\quad \mu = \E{x}
\end{equation}
where $\E{\cdot}$ denotes expectation; $x$ is the $p\times 1$ vector of real-valued instantaneous firing rates in bins of duration $\Delta t$; and $\mu$ is the vector of mean firing rates. In the case of noise correlations, $\mu$ depends on the stimulus condition.  The usual estimator of the covariance matrix is the \emph{sample covariance matrix} $C_{\sf 0}$ computed from the empirical sample of observations $x(t),\; t=n(1,\ldots,n)$ as
\begin{equation}
    C_{\sf 0} = \frac 1 \nu \sum\limits_{t=1}^n (x(t)-\bar x)(x(t)-\bar x)^\T,\quad \bar x= \frac 1 n \sum\limits_{t=1}^n x(t)
\end{equation}
where $\nu$ is the number of degrees of freedom per neuron in the sample ($\nu=n-1$ if observations are independent). In this study, we estimate the true mean, $\mu$,  using the sample mean $\bar x$, but seek a better estimate of the covariance matrix than $C_{\sf 0}$.

@@

Estimation can be improved through \emph{regularization}: the deliberate biasing of the estimate toward a low-dimensional approximation \cite{Schafer:2005,Bickel:2006}.  The sample estimate $C_{\sf 0}$ is unbiased ($\E{C_0}=\Sigma$) but, on average, falls far from $\Sigma$ due to its sensitivity to sampling noise.  Low-dimensional estimates are typically less susceptible to sampling noise but can introduce biases.  Regularization strikes a favorable balance between bias and variability, and can produce \emph{some} improvement even with an arbitrary target estimate.  Yet, when the target estimate captures important features of the true covariance matrix with few terms, a regularized estimate introduces minimal bias and outperforms other estimators.

@@

\begin{figure}[!ht]    \floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=8.3cm}}]{figure}[\FBwidth]
    {\caption{{\bf Illustration of regularized estimation of partial correlations.}
        {\bf A}. The sample correlation matrix of unprocessed somatic calcium signals from a population of cells in mouse visual cortex.
        The outlined square fragment is magnified in {\bf B}.
        {\bf C}. The same fragment of another estimate of the correlation matrix regularized to yield sparse partial correlations.
        Corresponding fragments of partial correlations matrices of the unregularized and regularized estimated are shown in {\bf D} and {\bf E}, respectively.
    }
    \label{fig:01}}
    {\includegraphics[width=8.3cm]{./figures/Figure01.pdf}}
\end{figure}
\paragraph{Model selection}
Covariance selection is but one of many conceivable low-dimensional approximations of the covariance matrix. Indeed any probabilistic model of the joint population activity regularized toward a small number of parameters automatically defines a low-dimensional approximation of the covariance matrix. Models that accurately reflect the dominant regularities in the activity of the circuit, its so-called `functional connectivity', tend to produce estimates that are nearest to the true value of the covariance matrix and are said to be more \emph{efficient} or to \emph{dominate} other estimators. An estimator's superior efficiency can be ascertained by cross-validation.  Because different types of neural circuits have different types of regularities in their activity, different probabilistic models and covariance matrix estimators may dominate in each case. The estimator that is shown to dominate all others for a specific type of neural circuit may provide the best descriptor of the low-dimensional representation of the correlation structure of the system of interest. Its structure may then be analyzed and related to the circuit's anatomical organization.  
\paragraph{Summary of findings}
In this study, we compared four regularized covariance matrix estimators biased toward different respective low-dimensional correlation structures: `shrinkage toward diagonal' or $C_{\sf diag}$, `shrinkage toward a multifactor model' or $C_{\sf factor}$, `sparse partial correlations' or $C_{\sf sparse}$, and `sparse partial correlations with latent units' or $C_{\sf sparse+latent}$.  First, we demonstrated that, in simulations with known true low-dimensional correlation structures, regularized estimators with matching types of low-dimensional structure generally dominated over the other estimators. We then used cross-validation to determine the most efficient estimator for the population activity of dense groups of neurons in mouse primary visual cortex. We found that $C_{\sf sparse+latent}$ consistently dominated the other estimators.  Estimate produced by $C_{\sf sparse+latent}$ revealed networks of interactions that differed substantially from networks of strongest correlations and depended strongly on the physical distance separating pairs of cells and on the differences in their preferred orientations.

@@

\paragraph{Covariance estimation in neural data}
We recorded calcium activity in dense populations of neurons in the supragranular layers in primary visual cortex of anesthetized mice using fast random-access 3D scanning two-photon microscopy \cite{Reddy:2005, Katona:2012, Cotton:2013}. We presented 300 repetitions of full-field drifting gratings with two directions of motion or 150 repetitions with five directions (\figref{03}{A}) on one side of the visual field of anesthetized mice. Groups of cells loaded with a calcium-sensitive fluorescent dye were imaged and localized in 3D space (\figref{03}{B and E} in the visual cortex on the contralateral side to the stimulus. Using acousto-optic deflectors (AOD) to steer the laser in 3D,  we recorded the somatic calcium activity from the located cells with concurrent motion detection \cite{Cotton:2013}.  This technique allowed fast sampling (100--150 Hz) from large numbers (150--350) of cells in a small volume of cortical tissue ($200\times200\times100$ $\mu$m$^3$) in layers 2/3 and 4 (\figref{03}{C}). After downsampling the signal to 20 Hz, relative firing rates were inferred using sparse nonnegative deconvolution \cite{Vogelstein:2010} (\figref{03}{C and D}). Only cells that produced detectable calcium activity were included in the analysis (See Methods). The average stimulus response was subtracted from each trial; the remaining signals were further downsampled into 150 ms bins to compute the noise correlation matrix (\figref{ 03}{F and G}). The durations of recordings dedicated to estimating the noise correlations ranged between 15--20 minutes.  Besides the high-repetition stimulus protocol used to estimate noise correlations, an orientation tuning stimulus protocol was used to map the orientation tuning of each cell (\figref{03}{E}). Overall, 31 imaged sites from 24 animals were included in the study.

@@

\section*{Methods}
% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\paragraph{Surgery and two-photon Imaging}
All procedures were conducted in accordance with the ethical guidelines of the National Institutes of Health and were approved by the Baylor College of Medicine IACUC.  The surgical procedures and data acquisition were performed as descrbed in \cite{Cotton:2013}. Briefly, C57BL/6J mice (aged p40--60) were used. Anesthesia was initiated with isoflurane (3%) and the mixture of fentanyl (0.05 mg/kg), midazolam (5 mg/kg), and medetomidine (0.5 mg/kg), with boosts of half the initial dose every 3 hours.  A craniotomy was performed over the right primary visual area.  Membrane-permeant calcium indicator Oregon Green 488 BAPTA-1 AM (OGB-1, Invitrogen) was loaded by bolus injection.  The craniotomy was sealed using a glass coverslip secured with dental cement.

Calcium imaging began 1 hour after dye injection.  All imaging was performed using the 3D-RAMP two-photon microscope described in \cite{Cotton:2013}. First, A 3D stack was acquired and cells manually segmented.  To collect calcium signals, the system repeated hopped between the selected neurons. 
\paragraph{Visual stimulus}
Full-field drifting gratings with 90\% contrast, luminance of 10 cd/m$^2$, spatial frequency of 0.08 cycles/degree, and temporal frequency of 2 cycles/s. Two sets of stimuli were presented for each imaging site: the first to map directional tuning and the second to estimate noise correlations. Directional tuning was map using a pseudo-random sequence of drifting gratings at sixteen equally spaced directional of motion changing at 2 Hz for 3 min without blanks. The data for covariance estimation were collected during presentations of full-field drifting gratings with the same parameters as those used in directional tuning except only two directions (in 9 dataset) or five directions (in 22 datasets) were used and the presentations lasted 1 second and, separated by 1-second blanks.  Each stimulus condition was presented at least 180 times. 
\paragraph{Data processing}
All data were processed in MATLAB using the DataJoint data processing chain toolbox ({\tt https://github.com/datajoint/}) developed in our lab.

@@

Since each of the regularized estimators had one or two hyperparameters, we used \emph{nested cross-validation}.  The outer loop evaluated the performance of the estimators with optimal values of the hyperparameters.  The optimization of the hyperparameters was performed within the inner loop in two phases: random search to find a good starting point and pattern search to find the global minimum.  The inner cross-validation loop subdivided the training dataset from the outer loop to perform 10-fold cross-validation in order to evaluate each choice of the hyperparameter values.  Thus the size of the training dataset within the inner loop comprised 81% of the entire recording.

>>>>

In this study, we sought most statistically efficient estimators of neural correlation matrices in recordings from large, dense groups of cortical neurons.  Using fast 3D random-access laser scanning microscopy of calcium signals, we recorded the activity of nearly every neuron in volumes of about 200 $\mu$m wide and 100 $\mu$m deep (150--350 cells) in mouse visual cortex.  We hypothesized that in these dense recordings, the correlation matrix would be most efficiently represented by a sparse network of partial correlations between pairs of observed neurons combined with common latent factors representing unobserved inputs and global network fluctuations.  Indeed, in cross-validation tests, the covariance matrix estimator based on such approximations outperformed other regularized estimators. Mirroring previously described patterns of synaptic connectivity, the density of positive partial correlations decreased rapidly with both physical distances and preferred orientation differences whereas negative partial correlations were less selective.  The inferred functional connectivity obtained using these methods can generate hypotheses about synaptic architecture that can guide future experimental work.

@@

Pearson correlations between the spiking activity of pairs of neurons, or simply \emph{neural correlations}, are among the most familiar descriptive statistics of neural population activity \cite{Averbeck:2006, Zohary:1994, Kohn:2005, Bair:2001, Ecker:2010}.  For example, \emph{noise correlations}, \emph{i.e.}~the correlations of trial-to-trial response variability between pairs of neurons, have a profound impact on stimulus coding \cite{Zohary:1994, Abbott:1999, Sompolinsky:2001, Averbeck:2006, Josic:2009, Berens:2011, Ecker:2011}. In addition, noise correlations and correlations in spontaneous activity have been hypothesized to reflect key features of functional connectivity in neural circuits and reflect interactions between neurons \cite{Gerstein:1964}.  This interpretation is supported by a series of discoveries of nontrivial relationships between neural correlations and other aspects of circuit organization such as the physical distances between neurons \cite{Smith:2008, Denman:2013}, their synaptic connectivity \cite{Ko:2011},  stimulus response similarity \cite{Bair:2001, Arieli:1995, Chiu:2002, Kenet:2003, Kohn:2005, Cohen:2008, Cohen:2009, Ecker:2010,Ko:2011, Smith:2013b}, cortical layer specificity \cite{Hansen:2012,Smith:2013}, progressive changes in development and in learning \cite{Golshani:2009, Gu:2011}, changes due to sensory stimulation and global brain states \cite{Goard:2009, Kohn:2009, Ecker:2010, Renart:2010}, and others.

@@

\paragraph{Additional information in neural correlation matrices}
Despite these ambiguities, a complete correlation matrix provides more information than the equivalent number of isolated pairwise correlations. In early studies, the effects of correlations were extrapolated from isolated pairs to entire populations through simulation and theoretical analysis \cite{Shadlen:1998, Zohary:1994}. In contrast, modern multineuronal recordings from increasingly large and dense populations of highly interconnected neurons allow estimation of various low-dimensional representations of the entire correlation matrix, which can enable inquiry into the nature of underlying physiological mechanisms and computational principles.

For example, one form of low-dimensional representation of the correlation matrix is its low-rank approximation. Such approximations are particularly suitable for capturing shared fluctuations across the recorded population, which may arise in local circuits or be externally driven. Low-rank components can be extracted using principal component or factor analysis. The resulting structure of neural correlations has been analyzed in a number of studies with particular attention paid to their temporal dynamics \cite{Yu:2009}.

@@

Conditional independence between a pair of variables suggests a lack of direct interaction between the underlying processes. Therefore, networks of partial correlations (sometimes called \emph{association networks}) can be used to infer interactions between the components of a complex system.  This approach has been used to uncover the structure of gene interaction networks \cite{Schafer:2005,Peng:2009} and the functional connectivity between brain regions from fMRI signals \cite{Varoquaux:2012,Ryali:2012}. In multivariate normal distributions (or, more generally, \emph{elliptical distributions}) interactions are completely defined by linear effects and, therefore, partial correlations reflect conditional dependencies.  A multivariate normal distribution specified by a weighted graph of non-zero partial correlations (along with the means and variances of individual neurons) is known as a Gaussian Graphical Model or Gauss-Markov Random Field \cite{Koller:2009}. With departure from linearity, the correspondence between conditional dependence and partial correlations diminishes and can break down \cite{Loh:2012}. For example, the coupling terms in pairwise Ising models do not directly correspond o the partial correlations \cite{Schneidman:2006, Tkacik:2006}.

@@

The true correlation matrix is the normalized version of the true covariance matrix defined as
\begin{equation}\label{eq:true-covariance}
    \Sigma = \E{(x-\mu)(x-\mu)^\T},\quad \mu = \E{x}
\end{equation}
where $\E{\cdot}$ denotes expectation; $x$ is the $p\times 1$ vector of real-valued instantaneous firing rates in bins of duration $\Delta t$; and $\mu$ is the vector of mean firing rates. In the case of noise correlations, $\mu$ depends on the stimulus condition.  Usually, neural covariance matrices have been estimated as the \emph{sample covariance matrix} $C_{\sf 0}$ calculated from the empirical sample of observations $x(t),\; t=n(1,\ldots,n)$ as
\begin{equation}
    C_{\sf 0} = \frac 1 \nu \sum\limits_{t=1}^n (x(t)-\bar x)(x(t)-\bar x)^\T,\quad \bar x= \frac 1 n \sum\limits_{t=1}^n x(t)
\end{equation}
where $\nu$ is the number of degrees of freedom per neuron in the sample ($\nu=n-1$ if observations are independent). In this study, we estimate the true mean, $\mu$,  using the sample mean $\bar x$, but seek a better estimate of the covariance matrix than $C_{\sf 0}$.

@@

Estimation can be improved through \emph{regularization}: deliberately imposing some kind of structure on the estimate. The sample estimate $C_{\sf 0}$, which is usually used to estimated covariance matrices in neuroscience, is unbiased ($\E{C_0}=\Sigma$).  However, on average, it falls far from $\Sigma$ due to its sensitivity to sampling noise.  Low-dimensional estimates are typically less susceptible to sampling noise but can introduce biases. Regularization strikes a favorable balance between bias and variability

 A regularized estimate is produced by biasing (`shrinking’) the estimate from the unbiased estimate toward a selected low-dimensional approximation (`target’) of the unbiased estimate \cite{Schafer:2005, Bickel:2006}.  The selection of the optimal target estimate and the optimal amount of shrinkage can be optimized based on the training data by analytical methods or by cross-validation.  However, some regularization schemes only perform target selection (\emph{dimensionality reduction}) and replace the estimate without shrinkages whereas others only perform shrinkage given a single target estimate (\emph{shrinkage estimators}).

Regularization can produce \emph{some} improvement even with an arbitrary target estimate (See Discussion).  Yet, when the target estimate captures important features of the true covariance matrix with few terms, a regularized estimate introduces minimal bias and outperforms other estimators.

@@

\begin{figure}[!ht]    \floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=8.3cm}}]{figure}[\FBwidth]
    {\caption{{\bf Illustration of regularized estimation of partial correlations.}
        {\bf A}. The sample correlation matrix of unprocessed somatic calcium signals from a population of cells in mouse visual cortex.
        The outlined square fragment is magnified in {\bf B}.
        {\bf C}. The same fragment of another estimate of the correlation matrix regularized to yield sparse partial correlations.
        Corresponding fragments of partial correlations matrices of the unregularized and regularized estimated are shown in {\bf D} and {\bf E}, respectively.
    }
    \label{fig:01}}
    {\includegraphics[width=8.3cm]{./figures/Figure01.pdf}}
\end{figure}
\paragraph{Model selection}
Covariance selection is but one of many conceivable low-dimensional approximations of the covariance matrix. Indeed any probabilistic model of the joint population activity regularized toward a small number of parameters automatically defines a low-dimensional approximation of the covariance matrix. Models that accurately reflect the dominant regularities in the activity of the circuit, its so-called `functional connectivity', tend to produce estimates that are nearest to the true value of the covariance matrix and are said to be more \emph{efficient} or to \emph{dominate} other estimators. An estimator's superior efficiency can be ascertained by cross-validation.  Because different types of neural circuits have different types of regularities in their activity, different probabilistic models and covariance matrix estimators may dominate in each case. The estimator that is shown to dominate all others for a specific type of neural circuit serves as an effective descriptor the circuit’s correlation structure.  This structure may then be analyzed with respect to the circuit's anatomical organization.
\paragraph{Summary of findings}
In this study, we compared four regularized covariance matrix estimators biased toward different respective low-dimensional correlation structures: `shrinkage toward diagonal' or $C_{\sf diag}$, `shrinkage toward a multifactor model' or $C_{\sf factor}$, `sparse partial correlations' or $C_{\sf sparse}$, and `sparse partial correlations with latent units' or $C_{\sf sparse+latent}$.  First, we demonstrated that, in simulations with known true low-dimensional correlation structures, regularized estimators with matching types of low-dimensional structure generally dominated over the other estimators. We then used cross-validation to determine the most efficient estimator for the population activity of dense groups of neurons in mouse primary visual cortex. We found that $C_{\sf sparse+latent}$ consistently dominated the other estimators.  Estimate produced by $C_{\sf sparse+latent}$ revealed networks of interactions that differed substantially from networks of strongest correlations and depended strongly on the physical distance separating pairs of cells and on the differences in their preferred orientations.

@@

\paragraph{Covariance estimation in neural data}
We recorded calcium activity in dense populations of neurons in the supragranular layers in primary visual cortex of anesthetized mice using fast random-access 3D scanning two-photon microscopy \cite{Reddy:2005, Katona:2012, Cotton:2013}. We presented 300 repetitions of full-field drifting gratings with two directions of motion or 150 repetitions with five directions (\figref{03}{A}) on one side of the visual field of anesthetized mice. Groups of cells loaded with a calcium-sensitive fluorescent dye were imaged and localized in 3D space (\figref{03}{B and E} in the visual cortex on the contralateral side to the stimulus. Using acousto-optic deflectors (AOD) to steer the laser in 3D,  we recorded the somatic calcium activity from the located cells with concurrent motion detection \cite{Cotton:2013}.  This technique allowed fast sampling (100--150 Hz) from large numbers (150--350) of cells in a small volume of cortical tissue ($200\times200\times100$ $\mu$m$^3$) in layers 2/3 and 4 (\figref{03}{C}). After downsampling the signal to 20 Hz, relative firing rates were inferred using sparse nonnegative deconvolution \cite{Vogelstein:2010} (\figref{03}{C and D}). Only cells that produced detectable calcium activity were included in the analysis (See Methods). The average stimulus response was subtracted from each trial; the remaining signals were further downsampled into 150 ms bins to compute the noise correlation matrix (\figref{03}{F and G}). The durations of recordings dedicated to estimating the noise correlations ranged between 15--20 minutes.  Besides the high-repetition stimulus protocol used to estimate noise correlations, an orientation tuning stimulus protocol was used to map the orientation tuning of each cell (\figref{03}{E}). Overall, 31 imaged sites from 24 animals were included in the study.

@@

\section*{Methods}
% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\paragraph{Surgery and two-photon Imaging}
All procedures were conducted in accordance with the ethical guidelines of the National Institutes of Health and were approved by the Baylor College of Medicine IACUC.  The surgical procedures and data acquisition were performed as descrbed in \cite{Cotton:2013}. Briefly, C57BL/6J mice (aged p40--60) were used. Anesthesia was initiated with isoflurane (3\%) and the mixture of fentanyl (0.05 mg/kg), midazolam (5 mg/kg), and medetomidine (0.5 mg/kg), with boosts of half the initial dose every 3 hours.  A craniotomy was performed over the right primary visual area.  Membrane-permeant calcium indicator Oregon Green 488 BAPTA-1 AM (OGB-1, Invitrogen) was loaded by bolus injection.  The craniotomy was sealed using a glass coverslip secured with dental cement.

Calcium imaging began 1 hour after dye injection.  All imaging was performed using the 3D-RAMP two-photon microscope described in \cite{Cotton:2013}. First, A 3D stack was acquired and cells manually segmented.  To collect calcium signals, the system repeated hopped between the selected neurons. 
\paragraph{Visual stimulus}
Full-field drifting gratings with 90\% contrast, luminance of 10 cd/m$^2$, spatial frequency of 0.08 cycles/degree, and temporal frequency of 2 cycles/s. Two sets of stimuli were presented for each imaging site: the first to map directional tuning and the second to estimate noise correlations. Directional tuning was map using a pseudo-random sequence of drifting gratings at sixteen equally spaced directional of motion changing at 2 Hz for 3 min without blanks. The data for covariance estimation were collected during presentations of full-field drifting gratings with the same parameters as those used in directional tuning except only two directions (in 9 dataset) or five directions (in 22 datasets) were used and the presentations lasted 1 second and, separated by 1-second blanks.  Each stimulus condition was presented at least 180 times. 
\paragraph{Data processing}
All data were processed in MATLAB using the DataJoint data processing chain toolbox ({\tt datajoint.github.com}) first developed in our lab.

@@

Since each of the regularized estimators had one or two hyperparameters, we used \emph{nested cross-validation}.  The outer loop evaluated the performance of the estimators with optimal values of the hyperparameters.  The optimization of the hyperparameters was performed within the inner loop in two phases: random search to find a good starting point and pattern search to find the global minimum.  The inner cross-validation loop subdivided the training dataset from the outer loop to perform 10-fold cross-validation in order to evaluate each choice of the hyperparameter values.  Thus the size of the training dataset within the inner loop comprised 81\% of the entire recording.
